### 2015-05-13 evaluation.tex
update in evaluation text

Using the race freedom guarantees that \whoop provides, we managed to significantly accelerate \corral in the majority of the cases. We noticed speedups between 1.5--20x.

A higher context-switch bound results into deeper interleavings being explored and thus a larger sequentialized program. Intuitively, this means that we see even greater speedups using information from \whoop, when exploring deeper interleavings.

>>>>

Using the race freedom guarantees that \whoop provides, we managed to significantly accelerate \corral in most of our benchmarks; the best performance was achieved using the \yieldmr instrumentation (see Table~\ref{tab:results}). Figure~\ref{fig:plot} shows that most of our speedups using \yieldmr are in the range of 1.5--10$\times$; whereas in two drivers, ssu100 and pc8736x\_gpio, we achieved $>$10$\times$ and $>$20$\times$ speedups, respectively (with csb of 9). We notice that a higher csb can result into greater speedups, when exploiting \whoop. This is expected, as a higher csb directly translates into a larger sequentialized program.
